Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-15 qpip.tex
Fix wording

	Ingredients:
	\begin{itemize}
		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
		\item Let $T$ be the number of gates in $C$.
		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
		\item Let $H_{C'(x)}=\sum_i \alpha_i H_i$ be the X-Z local Hamiltonian instance associated with the computation of $C'(x)$ from \Cref{thm:LHReduction}.
		\item Let $\histpsi{{C'(x)}}$ be the ground state of $H_{C'(x)}$.
		\item \XW{Let $s\leq n+2T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$ Why this number?} \Ethan{This number is used in de Finetti theorem. But I forgot to count ancilla, so it wasn't correct.}
		\item Let $\cVGS$ be the verification algorithm for $H_{C'(x)}$ as defined in \Cref{AlgGroundStateCheck}.
	\end{itemize}

>>>>

	Ingredients:
	\begin{itemize}
		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
		\item Let $T$ be the number of gates in $C$.
		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
		\item Let $H_{C'(x)}=\sum_i \alpha_i H_i$ be the X-Z local Hamiltonian instance associated with the computation of $C'(x)$ from \Cref{thm:LHReduction}.
		\item Let $\histpsi{{C'(x)}}$ be the ground state of $H_{C'(x)}$.
		\item \XW{Let $s\leq 3T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$ Why this number?} \Ethan{This is used in de Finetti theorem. But I forgot to count ancilla, so it wasn't correct before.}
		\item Let $\cVGS$ be the verification algorithm for $H_{C'(x)}$ as defined in \Cref{AlgGroundStateCheck}.
	\end{itemize}
